State-space analysis of continuous gravitational waves with a pulsar timing array: inclusion of the pulsar terms

### 2023-11-28 manuscript/manuscript_2/paper.tex
restart high strain bayes

% Abstract of the paper
\begin{abstract}	
	 Pulsar timing arrays may be able to detect continuous nanohertz gravitational waves emitted by individual supermassive black hole binaries. The gravitational wave (GW) signal is composed of two components, the ``Earth term" and ``pulsar term" which correspond to the GW incident on the Earth and the pulsar respectively. The data analysis procedure can be formulated within a state-space framework, wherein intrinsic achromatic spin wandering is Kalman-tracked concurrently with the modulation induced by a single-source gravitational wave in the pulse times of arrival. It is shown how to extend previous state-space analyses to include the pulsar terms. Astrophysically representative software injections in Gaussian measurement noise evidence that the inclusion of the pulsar terms eliminates the biases in the parameter estimates, increases the parameter accuracy, and decrease the minimal detectable strain relative to the previous approach. For a loud GW source with characteristic wave strain $h_0 = 10^{-12}$ the root-mean-square relative error in the estimated one-dimensional posteriors decreases by up to 99\% by including the pulsar terms. For a quiet GW source with $h_0 = 5 \times 10^{-15}$ there is no significant improvement in the parameter accuracy since the system is heavily noise dominated. However, including the pulsar terms decreases the minimal detectable strain by \textcolor{red}{Y percent} .
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}	
	 Pulsar timing arrays may be able to detect continuous nanohertz gravitational waves emitted by individual supermassive black hole binaries. The gravitational wave (GW) signal is composed of two components, the ``Earth term" and ``pulsar term" which correspond to the GW incident on the Earth and the pulsar respectively. The data analysis procedure can be formulated within a state-space framework, wherein intrinsic achromatic spin wandering is Kalman-tracked concurrently with the modulation induced by a single-source gravitational wave in the pulse times of arrival. It is shown how to extend previous state-space analyses to include the pulsar terms. Astrophysically representative software injections in Gaussian measurement noise evidence that for a loud GW source with characteristic wave strain $h_0 = 10^{-12}$ the inclusion of the pulsar terms decreases the root-mean-square relative error in the estimated one-dimensional posteriors by up to 99\%. For a quiet GW source with $h_0 = 5 \times 10^{-15}$ there is no significant improvement in the parameter accuracy since the system is heavily noise dominated. However, including the pulsar terms decreases the minimal detectable strain by \textcolor{red}{Y percent} .
\end{abstract}
